Improving INTEGRAL/SPI data analysis of GRBs

### 2022-02-03 src/ms.tex
add cite
fix

The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002. It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV. The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques+2003, Diehl+2006} and curvature in continuous spectra \citep{Jourdain-2020}.
%In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.

The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl+2003}. A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response. This method is used in several works which fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.

@@

\noindent
The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument. It is important to realize that the instruments SPI and GBM are fundamentally very similar. They both consist of individual detectors that have different responses for a given source position. In GBM, this is due to the different pointing directions of the detectors, and in SPI due to the varying obscuration by the mask. Even though SPI is defined as a coded-mask instrument, we don't have to treat it specially. The information which the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.

>>>>

The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002. It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV. The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques-2003, Diehl-2006} and curvature in continuous spectra \citep{Jourdain-2020}.
%In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.

The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl-2003}. A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response. This method is used in several works which fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.

@@

\noindent
The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument. It is important to realize that the instruments SPI and GBM are fundamentally very similar. They both consist of individual detectors that have different responses for a given source position. In GBM, this is due to the different pointing directions of the detectors, and in SPI due to the varying obscuration by the mask. Even though SPI is defined as a coded-mask instrument, we don't have to treat it specially. The information which the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method. A similar approach is used in \citet{Tohuvavohu-2021}, that introduces a new forward folding method to detect and localize faint GRBs with the coded mask instrument Swift/BAT.
